\maketitle
% \makesignature

\ifproject
\begin{abstract}
This term paper is a part of assignment of Modern Chinese Economy on the topic of 
"The China`s Technology and Economic Growth of China" to understand Chinese Economy.
That is important since China becomes the world`s economic and technological 
superpower. I am going to explain insight information about Chinese Technology by 
integrating various researches in order to obtain widespread information including 
references where I take it from. The key point is the heart of China's technological 
growth. Furthermore, I must realize and conclude them by summarizing to the last 
chapter. This finding is essential because Thailand should not stop growing, Thailand 
must keep running and moving forward China. 

\end{abstract}

\iffalse
\begin{dedication}
This document is dedicated to all Chiang Mai University students.

Dedication page is optional.
\end{dedication}
\fi % \iffalse

\begin{acknowledgments}

I would like to express my heartfelt acknowledgment of the remarkable technological 
and economic progress achieved by the People's Republic of China. Over the past few 
decades, China has undergone an extraordinary transformation, emerging as a global 
powerhouse in both technology and economics. 

I extend my appreciation to the Chinese government, entrepreneurs, scientists, and 
the entire Chinese population for their relentless pursuit of excellence and their 
enduring contributions to the advancement of technology and economic development. 
The lessons learned from China's experience serve as an inspiration and valuable 
reference point for nations seeking to achieve similar progress.

\texttt{acknowledgment} environment.

\acksign{2023}{10}{7}
\end{acknowledgments}%
\fi % \ifproject

\contentspage

\ifproject
\figurelistpage

\tablelistpage
\fi % \ifproject

% \abbrlist % this page is optional

% \symlist % this page is optional

% \preface % this section is optional
